---
title: "WQ Station Trend Tests & Display"
author: "Ed Sherwood <esherwood@epchc.org>"
date: "December 14, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(leaflet)
library(lubridate)
library(rkt)
```

## Import Station Data

Download water quality data from USF Water Atlas site in text (tab delimited format).

```{r MC Water Quality}
mc_data <- read_delim("G:/Ed/GIT_Projects/wq_station_trends/MC_River-Stream_Stations.txt", "\t", escape_double = FALSE, col_types = cols(SampleDate = col_datetime(format = "%m/%d/%Y %H:%M:%S AM")), trim_ws = TRUE)
View(mc_data)
```

## Identify sites on a Map

Show a simple map of the water quality sites.

```{r wq site map, echo=FALSE}
wqsites <- mc_data %>% 
           select(StationName, WaterBodyName, Actual_Latitude, Actual_Longitude) %>% 
           unique()

map <- leaflet(wqsites) %>% 
              addProviderTiles(providers$CartoDB.Positron) %>% 
              addCircleMarkers(~Actual_Longitude, ~Actual_Latitude,
                               radius = 6,
                               stroke = FALSE,
                               color = ~WaterBodyName,
                               popup = ~as.character(paste('MC Station:', StationName)))
map
```

## Run Seasonal Kendall-Tau Trend Tests on Individual Stations
No QA/QC checks performed. Just a straight analysis of individual station POR data on TN values, as stored in the USF Water Atlas Site.

```{r}
mc_data$mo <- month(mc_data$SampleDate)
mc_data$yr <- decimal_date(mc_data$SampleDate)


ggplot(mc_data, aes(SampleDate, Result_Value)) + 
  geom_point() +
  facet_wrap(~StationName) +
  ylab("Total Nitrogen (ug/L)") +
  xlab("Date")

#Plot results for each station individually
for(var in unique(mc_data$StationName)) {
  dev.new()
  print( ggplot(mc_data[mc_data$StationName==var,], 
                aes(SampleDate, Result_Value)) + 
                geom_point() +
                ggtitle(var) +
                ylab("Total Nitrogen (ug/L)") +
                xlab("Date"))
}

#Perform the Seasonal Kendall Tau Trend Test on Each Station

datalist = list()

for(var in unique(mc_data$StationName)) {
  dat <- mc_data %>% 
         filter(StationName == var)
  out <- rkt(dat$yr, dat$Result_Value, dat$mo,correct=T, rep="a")
  out$StationName <- var
  datalist[[var]] <- out
}

all <- data.table::rbindlist(datalist)

all <- all %>%
       select(StationName, sl.corrected, sl, tau) %>% 
       left_join(wqsites,all, by = "StationName")

results <- all

results$sl.corrected[is.na(results$sl.corrected)] <- results$sl

attach(results)
results$trend[results$tau > 0] <- "Up"
results$trend[results$tau < 0] <- "Down"

results$sig[results$sl.corrected > 0.05] <- "NS"
results$sig[results$sl.corrected <= 0.05] <- "Lo"
results$sig[results$sl.corrected <= 0.01] <- "Hi"

results$trend[results$sig == "NS"] <- ""

results$id <- as.factor(paste(results$trend, results$sig, sep = "")) 
detach(results)

results$icon <- ifelse(results$id %in% c("NANA", "NALo", "NAHi", "NS", NA), "NS",
                  ifelse(results$id == "DownLo", "GrDoLo",
                   ifelse(results$id == "DownHi", "GrDoHi",
                    ifelse(results$id == "UpLo", "ReUpLo",                
                     ifelse(results$id == "UpHi", "ReUpHi", NA)))))
                  

#Create some fancy icons for the map
trendicons <- iconList(
  GrDoLo = makeIcon("./green-down-arrow-icon-44134.png","./green-down-arrow-icon-44134.png", 12, 12),
  GrDoHi = makeIcon("./green-down-arrow-icon-44134.png", "./green-down-arrow-icon-44134.png", 24, 24),
  ReUpLo = makeIcon("./red-arrow-up-674833.png","./red-arrow-up-674833.png", 12, 12),
  ReUpHi = makeIcon("./red-arrow-up-674833.png", "./red-arrow-up-674833.png", 24, 24),
  NS = makeIcon("./Circle-icon.png","./Circle-icon.png", 12, 12)
  )
  
html_legend <- "<H4>Manatee County WQ Trends</H4><br/><img src = 'http://www.tbeptech.org/DATA/icons/green-down-arrow-icon-44134.png' height='12' width='12'>Decreasing, Lo Sig.<br/><img src = 'http://www.tbeptech.org/DATA/icons/green-down-arrow-icon-44134.png' height='24' width='24'>Decreasing, Hi Sig.<br/><img src = 'http://www.tbeptech.org/DATA/icons/red-arrow-up-674833.png' height='12' width='12'>Increasing, Lo Sig.<br/><img src = 'http://www.tbeptech.org/DATA/icons/red-arrow-up-674833.png' height='24' width='24'>Decreasing, Hi Sig.<br/><img src = 'http://www.tbeptech.org/DATA/icons/Circle-icon.png' height='12' width='12'>No Trend"

resultmap <- leaflet(results) %>% 
              addProviderTiles(providers$CartoDB.Positron) %>%
              #addTiles()  
              addMarkers(~Actual_Longitude, ~Actual_Latitude,icon = ~trendicons[icon], label = ~StationName) %>% 
              addControl(html = html_legend, position = "bottomleft")
resultmap

```


